Literature

### 2015-08-12 literature/literature.Rmd
fiddling with the literature

They mention few investigations, most of them uses n-grams. The `r citet(refs[["wang_application_2000"]])` was the most appealing.

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs[["yang_alignment_2013"]])))
```

@@

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
sort(refs, sorting = "ynt")
```

>>>>

They mention few investigations, most of them uses n-grams. The `r tmp <- citet(refs[["wang_application_2000"]])` was the most appealing.

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs["yang_alignment_2013"])))
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='markup'}
search()

works.cited
```

@@
